Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex

The Immune Epitope Database (IEDB) from the National Institutes of Health contains millions of linear epitope sequences obtained
by an MHC ligand assay.
For the MHC alleles used in this study, 
we obtained 54,303 and 2,484 linear epitope sequences for the MHC-I
and MHC-II alleles respectively.
There are relatively few epitopes for MHC-II, 
as MHC-II has many more different alleles than MHC-I,
whereas we selected only the epitopes found for the 21 MHC-II alleles used in this study.

Figure \ref{fig:2a} shows that there are similar levels of
over-presentation of TMH-derived epitopes between (1) the
percentage of TMH-derived epitopes that is reported in the IEDB database
versus (2) the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in an informative figure.

>>>>

The Immune Epitope Database (IEDB) from the National Institutes of Health contains millions of linear epitope sequences obtained
by an MHC ligand assay.
For the MHC alleles used in this study, 
we obtained 54,303 and 2,484 linear epitope sequences for the MHC-I
and MHC-II alleles from human origin respectively.
There are relatively few epitopes for MHC-II, 
as MHC-II has many more different alleles than MHC-I,
whereas we selected only the human epitopes found for the 21 MHC-II alleles used in this study.

Figure \ref{fig:2a} shows that there are similar levels of
over-presentation of TMH-derived epitopes between (1) the
percentage of TMH-derived epitopes that is reported in the IEDB database
versus (2) the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in an informative figure. 
We showed that there is a correlation between epitopes taken from
predicted 9-mers (for MHC-I) and 14-mers (for MHC-II) from a human
reference proteome and epitopes taken from the IEDB for MHC ligands
essays (see in Supplementary figure \ref{fig:thm_presentation_correlation}).
